Software Ticket Quality

### 2017-11-15 proposal/mprop.tex
Add paper on extracting info from bug reports

\textbf{Product perspective on total 
        Data Quality Assessment}\cite{wang1998product}:
\begin{itemize}
  \item \textbf{What were the goals?}

@@

>>>>

% TODO: complete this paper
\textbf{Product perspective on total 
        Data Quality Assessment}\cite{wang1998product}:
\begin{itemize}
  \item \textbf{What were the goals?}

@@

\textbf{Extracting Structural Information from Bug Reports}\cite{bettenburg2008extracting}:
\begin{itemize}
  \item \textbf{What were the goals?}
    The authors try to present a tool called infoZilla that can accurately
    extract different types of information (e.g. stack traces, source code
    fragments) from bug reports.
  \item \textbf{What was the method?}
    They selected a few categories of information that both infoZilla could
    successfully extract from bug reports and that are of most interest to developers. Thus,
    the categories selected are:
      \begin{itemize}
        \item patches;
        \item stack traces;
        \item source code;
        \item enumerations.
      \end{itemize}
    Then, they ran the tool on tickets and evaluated the overall accuracy.
  \item \textbf{What did they learn?}
    After developing the tool to inspect such elements and retrieve them, 
    they evaluated it on over 160000 Eclipse bug reports. For all categories, infoZilla
    achieved over 97\% accuracy. 
  \item \textbf{Relevance to our work}:
    If we could manage to get this tool and use it in our own research, it would be
    beneficial as we could extract efficiently different types of information we are
    interested in testing ticket quality (e.g. stack traces).
\end{itemize}
